---
title: "2025.07.07 analysis"
author: "Simon Cooper"
format: pdf
editor: visual
---

## 2025.07.07 Analysis

### 0. Set-up. 

```{r setup, include = FALSE}

# Clearing environment.
rm(list=ls())

# Setting working directory.
setwd("/Users/simoncooper/Documents/measles")

# Loading data.
load("clean_brazil_data(1).RData")

# Loading relevant packages.
library(tidyverse)

```

### 1. Time series figures.

#### National: measles vaccine coverage, cases, and deaths.

```{r}

# Calculating measles vaccine coverage, cases, and deaths.
nat_avg_vax <- df %>%
  group_by(year) %>%
  summarize(weighted_avg_coverage = weighted.mean(coverage, population, na.rm = TRUE))

nat_cases_prop <- df %>%
  filter(year >= 2001) %>% # Note: case data doesn't start until 2001, which is why I'm excluding it from the time series here.
  group_by(year) %>%
  summarize(total_cases_prop = (sum(measles_cases)/sum(population) * 100000))

nat_deaths_prop <- df %>%
  group_by(year) %>%
  summarize(
    total_deaths = sum(measles_deaths),
    total_deaths_prop = (sum(measles_deaths)/sum(population) * 100000))

# Combining data in one place.
nat_vax_cases_deaths <- nat_avg_vax %>%
  left_join(nat_cases_prop, by = "year") %>%
  left_join(nat_deaths_prop, by = "year")

# Plotting.
ggplot(nat_vax_cases_deaths, aes(x = year)) +
  geom_line(aes(y = weighted_avg_coverage, color = "Vaccination Coverage")) +
  geom_line(aes(y = total_cases_prop, color = "Measles Cases per 100k")) + 
  geom_line(aes(y = total_deaths_prop, color = "Measles Deaths per 100k")) +
  scale_y_continuous(name = "Measles Vaccination Coverage (%)",
                     sec.axis = sec_axis(~ . * max(nat_vax_cases_deaths$total_cases_prop, na.rm = TRUE) / 100, name = "Cases/Deaths per 100,000")) + 
  labs(x = "Year",
       title = "Vaccination Coverage, Cases, and Deaths (1996-2023)", 
       color = "Metric")

```

#### Regional: measles vaccine coverage, cases, and deaths.

```{r}

# Calculating measles vaccine coverage, cases, and deaths.
regions_avg_vax <- df %>%
  group_by(year, region) %>%
  summarize(weighted_avg_coverage = weighted.mean(coverage, population, na.rm = TRUE))

regions_cases_prop <- df %>%
  filter(year >= 2001) %>% # Note: case data doesn't start until 2001, which is why I'm excluding it from the time series here.
  group_by(year, region) %>%
  summarize(total_cases_prop = (sum(measles_cases)/sum(population) * 100000))

regions_deaths_prop <- df %>%
  group_by(year, region) %>%
  summarize(total_deaths_prop = (sum(measles_deaths)/sum(population) * 100000))

# Combining data in one place.
regions_vax_cases_deaths <- regions_avg_vax %>%
  left_join(regions_cases_prop, by = c("year", "region")) %>%
  left_join(regions_deaths_prop, by = c("year", "region"))

# Plotting.
ggplot(regions_vax_cases_deaths, aes(x = year)) +
  geom_line(aes(y = weighted_avg_coverage, color = "Vaccination Coverage")) +
  geom_line(aes(y = total_cases_prop, color = "Measles Cases per 100k")) + 
  geom_line(aes(y = total_deaths_prop, color = "Measles Deaths per 100k")) +
  facet_wrap(~region) +
  scale_y_continuous(name = "Measles Vaccination Coverage (%)",
                     sec.axis = sec_axis(~ . * max(regions_vax_cases_deaths$total_cases_prop, na.rm = TRUE) / 100, name = "Cases/Deaths per 100,000")) + 
  labs(x = "Year",
       title = "Vaccination Coverage, Cases, and Deaths by Region (1996-2023)", 
       color = "Metric")

```

### 2. Correlations with 2 and 4 year lags.

National: correlations, 2 years.

```{r}

# Calculating correlation between vaccination coverage and measles cases.
correlations_cases_2yrs_outbreak1 <- df %>%
  arrange(year) %>%
  filter(year >= 2011 & year <= 2015) %>%
  summarize(correlation = cor(lag(coverage, n = 2), measles_cases, use = "complete.obs"),
            n_obs = sum(!is.na(lag(coverage, n = 2)) & !is.na(measles_cases)))
correlations_cases_2yrs_outbreak1

correlations_cases_2yrs_outbreak2 <- df %>%
  arrange(year) %>%
  filter(year >= 2016 & year <= 2021) %>%
  summarize(correlation = cor(lag(coverage, n = 2), measles_cases, use = "complete.obs"),
            n_obs = sum(!is.na(lag(coverage, n = 2)) & !is.na(measles_cases)))
correlations_cases_2yrs_outbreak2

# Calculating correlation between vaccination coverage and measles deaths.
correlations_deaths_2yrs_outbreak1 <- df %>%
  arrange(year) %>%
  filter(year >= 2011 & year <= 2015) %>%
  summarize(correlation = cor(lag(coverage, n = 2), measles_deaths, use = "complete.obs"),
            n_obs = sum(!is.na(lag(coverage, n = 2)) & !is.na(measles_deaths)))
correlations_deaths_2yrs_outbreak1

correlations_deaths_2yrs_outbreak2 <- df %>%
  arrange(year) %>%
  filter(year >= 2016 & year <= 2021) %>%
  summarize(correlation = cor(lag(coverage, n = 2), measles_deaths, use = "complete.obs"),
            n_obs = sum(!is.na(lag(coverage, n = 2)) & !is.na(measles_deaths)))
correlations_deaths_2yrs_outbreak2

```

National: correlations, 4 years.

```{r}

# Calculating correlation between vaccination coverage and measles cases.
correlations_cases_4yrs_outbreak1 <- df %>%
  arrange(year) %>%
  filter(year >= 2009 & year <= 2015) %>%
  summarize(correlation = cor(lag(coverage, n = 4), measles_cases, use = "complete.obs"),
            n_obs = sum(!is.na(lag(coverage, n = 4)) & !is.na(measles_cases)))
correlations_cases_4yrs_outbreak1

correlations_cases_4yrs_outbreak2 <- df %>%
  arrange(year) %>%
  filter(year >= 2014 & year <= 2021) %>%
  summarize(correlation = cor(lag(coverage, n = 4), measles_cases, use = "complete.obs"),
            n_obs = sum(!is.na(lag(coverage, n = 4)) & !is.na(measles_cases)))
correlations_cases_4yrs_outbreak2

# Calculating correlation between vaccination coverage and measles deaths.
correlations_deaths_4yrs_outbreak1 <- df %>%
  arrange(year) %>%
  filter(year >= 2009 & year <= 2015) %>%
  summarize(correlation = cor(lag(coverage, n = 4), measles_deaths, use = "complete.obs"),
            n_obs = sum(!is.na(lag(coverage, n = 4)) & !is.na(measles_deaths)))
correlations_deaths_4yrs_outbreak1

correlations_deaths_4yrs_outbreak2 <- df %>%
  arrange(year) %>%
  filter(year >= 2014 & year <= 2021) %>%
  summarize(correlation = cor(lag(coverage, n = 4), measles_deaths, use = "complete.obs"),
            n_obs = sum(!is.na(lag(coverage, n = 4)) & !is.na(measles_deaths)))
correlations_deaths_4yrs_outbreak2

```

Regional: correlations, 2 years.

```{r}

# Calculating correlation between vaccination coverage and measles cases.
region_correlations_cases_2yrs_outbreak1 <- df %>%
  arrange(region, year) %>%
  filter(year >= 2011 & year <= 2015) %>%
  group_by(region) %>%
  summarize(correlation = cor(lag(coverage, n = 2), measles_cases, use = "complete.obs"),
            n_obs = sum(!is.na(lag(coverage, n = 2)) & !is.na(measles_cases)),
            .groups = "drop")
region_correlations_cases_2yrs_outbreak1

region_correlations_cases_2yrs_outbreak2 <- df %>%
  arrange(region, year) %>%
  filter(year >= 2016 & year <= 2021) %>%
  group_by(region) %>%
  summarize(correlation = cor(lag(coverage, n = 2), measles_cases, use = "complete.obs"),
            n_obs = sum(!is.na(lag(coverage, n = 2)) & !is.na(measles_cases)),
            .groups = "drop")
region_correlations_cases_2yrs_outbreak2

# Calculating correlation between vaccination coverage and measles deaths.
region_correlations_deaths_2yrs_outbreak1 <- df %>%
  arrange(region, year) %>%
  filter(year >= 2011 & year <= 2015) %>%
  group_by(region) %>%
  summarize(correlation = cor(lag(coverage, n = 2), measles_deaths, use = "complete.obs"),
            n_obs = sum(!is.na(lag(coverage, n = 2)) & !is.na(measles_deaths)),
            .groups = "drop")
region_correlations_deaths_2yrs_outbreak1

region_correlations_deaths_2yrs_outbreak2 <- df %>%
  arrange(region, year) %>%
  filter(year >= 2016 & year <= 2021) %>%
  group_by(region) %>%
  summarize(correlation = cor(lag(coverage, n = 2), measles_deaths, use = "complete.obs"),
            n_obs = sum(!is.na(lag(coverage, n = 2)) & !is.na(measles_deaths)),
            .groups = "drop")
region_correlations_deaths_2yrs_outbreak2

```

Regional: correlations, 4 years.

```{r}

# Calculating correlation between vaccination coverage and measles cases.
region_correlations_cases_4yrs_outbreak1 <- df %>%
  arrange(region, year) %>%
  filter(year >= 2009 & year <= 2015) %>%
  group_by(region) %>%
  summarize(correlation = cor(lag(coverage, n = 4), measles_cases, use = "complete.obs"),
            n_obs = sum(!is.na(lag(coverage, n = 4)) & !is.na(measles_cases)),
            .groups = "drop")
region_correlations_cases_4yrs_outbreak1

region_correlations_cases_4yrs_outbreak2 <- df %>%
  arrange(region, year) %>%
  filter(year >= 2014 & year <= 2021) %>%
  group_by(region) %>%
  summarize(correlation = cor(lag(coverage, n = 4), measles_cases, use = "complete.obs"),
            n_obs = sum(!is.na(lag(coverage, n = 4)) & !is.na(measles_cases)),
            .groups = "drop")
region_correlations_cases_4yrs_outbreak2

# Calculating correlation between vaccination coverage and measles deaths.
region_correlations_deaths_4yrs_outbreak1 <- df %>%
  arrange(region, year) %>%
  filter(year >= 2009 & year <= 2015) %>%
  group_by(region) %>%
  summarize(correlation = cor(lag(coverage, n = 4), measles_deaths, use = "complete.obs"),
            n_obs = sum(!is.na(lag(coverage, n = 4)) & !is.na(measles_deaths)),
            .groups = "drop")
region_correlations_deaths_4yrs_outbreak1

region_correlations_deaths_4yrs_outbreak2 <- df %>%
  arrange(region, year) %>%
  filter(year >= 2014 & year <= 2021) %>%
  group_by(region) %>%
  summarize(correlation = cor(lag(coverage, n = 4), measles_deaths, use = "complete.obs"),
            n_obs = sum(!is.na(lag(coverage, n = 4)) & !is.na(measles_deaths)),
            .groups = "drop")
region_correlations_deaths_4yrs_outbreak2

```

### 3. Scatter plots: cases/deaths against percent urban by outbreak by region.

National, cases and deaths, 2013-2015.

```{r}

outbreak_2013to2015 <- df %>%
  filter(year %in% 2013:2015) %>%
  group_by(muni_code) %>%
  summarize(measles_cases_p100k_sum = sum(measles_cases_p100k, na.rm = T),
            measles_deaths_p100k_sum = sum(measles_deaths_p100k, na.rm = T),
            pct_urban_2010 = first(pct_urban_2010),
            region = first(region),
            .groups = "drop")

# Plotting cases.  
ggplot(outbreak_2013to2015, aes(x = pct_urban_2010, y = measles_cases_p100k_sum)) +
  geom_point(shape = 1, na.rm = T) +
  labs(
    x = "Percent Urban (2010)",
    y = "Measles Cases per 100,000 People",
    title = "Prevalence of Measles Cases by Level of Urbanization, 2013-2015 Outbreak")

# Plotting deaths.
ggplot(outbreak_2013to2015, aes(x = pct_urban_2010, y = measles_deaths_p100k_sum)) +
  geom_point(shape = 1, na.rm = T) +
  labs(
    x = "Percent Urban (2010)",
    y = "Measles Deaths per 100,000 People",
    title = "Prevalence of Measles Deaths by Level of Urbanization, 2013-2015 Outbreak")

```

National, cases and deaths, 2018-2021.

```{r}

outbreak_2018to2021 <- df %>%
  filter(year %in% 2018:2021) %>%
  group_by(muni_code) %>%
  summarize(measles_cases_p100k_sum = sum(measles_cases_p100k, na.rm = T),
            measles_deaths_p100k_sum = sum(measles_deaths_p100k, na.rm = T),
            pct_urban_2010 = first(pct_urban_2010),
            region = first(region),
            .groups = "drop")

# Plotting cases.  
ggplot(outbreak_2018to2021, aes(x = pct_urban_2010, y = measles_cases_p100k_sum)) +
  geom_point(shape = 1, na.rm = T) +
  labs(
    x = "Percent Urban (2010)",
    y = "Measles Cases per 100,000 People",
    title = "Prevalence of Measles Cases by Level of Urbanization, 2018-2021 Outbreak")

# Plotting deaths.
ggplot(outbreak_2018to2021, aes(x = pct_urban_2010, y = measles_deaths_p100k_sum)) +
  geom_point(shape = 1, na.rm = T) +
  labs(
    x = "Percent Urban (2010)",
    y = "Measles Deaths per 100,000 People",
    title = "Prevalence of Measles Deaths by Level of Urbanization, 2018-2021 Outbreak")

```

Regional, cases and deaths, 2013-2015.

```{r}

# Cases.
ggplot(outbreak_2013to2015, aes(x = pct_urban_2010, y = measles_cases_p100k_sum)) +
  geom_point(shape = 1, na.rm = T) +
  facet_wrap(~region) +
  labs(
    x = "Percent Urban (2010)",
    y = "Measles Cases per 100,000 People",
    title = "Prevalence of Measles Cases by Level of Urbanization, 2013-2015 Outbreak")

# Deaths.
ggplot(outbreak_2013to2015, aes(x = pct_urban_2010, y = measles_deaths_p100k_sum)) +
  geom_point(shape = 1, na.rm = T) +
  facet_wrap(~region) +
  labs(
    x = "Percent Urban (2010)",
    y = "Measles Deaths per 100,000 People",
    title = "Prevalence of Measles Deaths by Level of Urbanization, 2013-2015 Outbreak")

```

Regional, cases and deaths, 2018-2021.

```{r}

# Cases.
ggplot(outbreak_2018to2021, aes(x = pct_urban_2010, y = measles_cases_p100k_sum)) +
  geom_point(shape = 1, na.rm = T) +
  facet_wrap(~region) +
  labs(
    x = "Percent Urban (2010)",
    y = "Measles Cases per 100,000 People",
    title = "Prevalence of Measles Cases by Level of Urbanization, 2018-2021 Outbreak")

# Deaths.
ggplot(outbreak_2018to2021, aes(x = pct_urban_2010, y = measles_deaths_p100k_sum)) +
  geom_point(shape = 1, na.rm = T) +
  facet_wrap(~region) +
  labs(
    x = "Percent Urban (2010)",
    y = "Measles Deaths per 100,000 People",
    title = "Prevalence of Measles Deaths by Level of Urbanization,  2018-2021 Outbreak")

```
