---
title: "xx. Analysis Plan"
author: "Simon Cooper"
format: html
editor: visual
---

# Analysis Plan

## 0. Set-up.

#### 0.1. Clearing environment, loading relevant packages.

```{r}

rm(list=ls())

library(dplyr)
library(ggplot2)
library(tidyr)
library(zoo)
library(gridExtra)
library(MASS)
library(AER)
library(glmmTMB)
library(ggeffects)
library(performance)
library(broom.mixed)
library(purrr)
library(plm)
library(pglm)
library(glmmTMB)
library(dagitty)

options(scipen = 999) # Turning off scientific notation.

```

#### 0.2. Loading data.

```{r}

load("clean_brazil_data.RData")

```

## 1. Descriptive visualizations.

### 1.1. Plot measles dose 1 and dose 2 vaccination rates and measles cases (different y-axes).

#### 1.1.1. National.

```{r}

# Calculating measles vaccine coverage, cases, and deaths.
nat_avg_vax <- df %>%
  filter(year >= 2001) %>%
  group_by(year) %>%
  summarize(weighted_avg_coverage1 = weighted.mean(coverage_dose1, population, na.rm = TRUE),
            weighted_avg_coverage2 = weighted.mean(coverage_dose2, population, na.rm = TRUE))

nat_cases_prop <- df %>%
  filter(year >= 2001) %>% 
  group_by(year) %>%
  summarize(total_cases_prop = (sum(measles_cases)/sum(population) * 100000))

# Combining data in one place.
nat_vax_cases <- nat_avg_vax %>%
  left_join(nat_cases_prop, by = "year")

# Plotting.
ggplot(nat_vax_cases, aes(x = year)) +
  geom_line(aes(y = weighted_avg_coverage1, color = "Vaccination Dose 1 Coverage")) +
  geom_line(aes(y = weighted_avg_coverage2, color = "Vaccination Dose 2 Coverage")) +
  geom_line(aes(y = total_cases_prop, color = "Measles Cases per 100k")) + 
  scale_y_continuous(name = "Measles Vaccination Coverage (%)",
                     sec.axis = sec_axis(~ . * max(nat_vax_cases$total_cases_prop, na.rm = TRUE) / 100, name = "Cases per 100,000")) + 
  labs(x = "Year",
       title = "Vaccination Coverage and Cases (2001-2023)", 
       color = "Metric")

```

#### 1.1.2. Regional.

Check whether the coverage data at the regional level.

Just to check what we're getting at the regional level is the smae.

```{r}

# Calculating measles vaccine coverage, cases, and deaths.
regions_avg_vax <- df %>%
  filter(year >= 2001) %>%
  group_by(year, region) %>%
  summarize(weighted_avg_coverage1 = weighted.mean(coverage_dose1, population, na.rm = TRUE),
            weighted_avg_coverage2 = weighted.mean(coverage_dose2, population, na.rm = TRUE))

regions_cases_prop <- df %>%
  filter(year >= 2001) %>% 
  group_by(year, region) %>%
  summarize(total_cases_prop = (sum(measles_cases)/sum(population) * 100000))

# Combining data in one place.
regions_vax_cases <- regions_avg_vax %>%
  left_join(regions_cases_prop, by = c("year", "region"))

# Plotting.
ggplot(regions_vax_cases, aes(x = year)) +
  geom_line(aes(y = weighted_avg_coverage1, color = "Vaccination Dose 1 Coverage")) +
  geom_line(aes(y = weighted_avg_coverage2, color = "Vaccination Dose 2 Coverage")) +
  geom_line(aes(y = total_cases_prop, color = "Measles Cases per 100k")) + 
  facet_wrap(~region) +
  scale_y_continuous(name = "Measles Vaccination Coverage (%)",
                     sec.axis = sec_axis(~ . * max(regions_vax_cases$total_cases_prop, na.rm = TRUE) / 100, name = "Cases per 100,000")) + 
  labs(x = "Year",
       title = "Vaccination Coverage and Cases (2001-2023)", 
       color = "Metric")

```

### 1.2. Map cumulative measles cases \[ask for help\].

### 1.3. Calculate and map measles susceptible population.

#### 1.3.1. Calculate measles susceptible population.

##### 1.3.1.1. Preparation.

```{r}

# Calculating version of coverage variables that is top coded to 100.
df <- df %>%
  group_by(muni_code, year) %>%
  mutate(
    tc_coverage_dose1_lag1 = pmin(coverage_dose1_lag1, 100),
    tc_coverage_dose1_lag2 = pmin(coverage_dose1_lag2, 100),
    tc_coverage_dose1_lag3 = pmin(coverage_dose1_lag3, 100),
    tc_coverage_dose1_lag4 = pmin(coverage_dose1_lag4, 100),
    tc_coverage_dose1_lag5 = pmin(coverage_dose1_lag5, 100),
    tc_coverage_dose1_lag6 = pmin(coverage_dose1_lag6, 100),
    tc_coverage_dose1_lag7 = pmin(coverage_dose1_lag7, 100),
    tc_coverage_dose1_lag8 = pmin(coverage_dose1_lag8, 100),
    tc_coverage_dose1_lag9 = pmin(coverage_dose1_lag9, 100)) %>%
  ungroup()

# Noticed that there was lots of missingness. Checking where it's coming from.
sapply(df[c("births", "deaths_U6mo", "pop_one", "pop_two", "pop_three", "pop_four", "pop_five", 
            "pop_six", "pop_seven", "pop_eight", "pop_nine", "tc_coverage_dose1_lag1", "tc_coverage_dose1_lag2", 
            "tc_coverage_dose1_lag3", "tc_coverage_dose1_lag4", "tc_coverage_dose1_lag5", "tc_coverage_dose1_lag6", "tc_coverage_dose1_lag7",
            "tc_coverage_dose1_lag8", "tc_coverage_dose1_lag9")], function(x) sum(is.na(x)))

# Age-structured population data is missing for some municipality-year combos. Restricting data to municipality-year combos with  age-structured population data.
vars <- c("births", "deaths_U6mo", "pop_one", "pop_two", "pop_three", "pop_four", "pop_five", 
          "pop_six", "pop_seven", "pop_eight", "pop_nine")
df <- df[complete.cases(df[vars]), ]

```

##### 1.3.1.2. Calculations (two versions).

```{r}

# Version 1: Accounting for infection-acquired immunity and assuming that all measles cases happen among children under 10.

df <- df %>%
  group_by(muni_code) %>%
  arrange(year) %>%
  mutate(across(c(births, deaths_U6mo, pop_one:pop_nine, tc_coverage_dose1_lag1:tc_coverage_dose1_lag9, measles_cases), 
                ~replace_na(., 0))) %>%
  mutate(cumulative_10yr_cases = lag(rollapply(measles_cases, width = 10, FUN = sum, fill = 0, align = "right", partial = TRUE), default = 0),
         susceptible_pop1 = pmax(0, (births - deaths_U6mo) + 
                                   pop_one*(100 - tc_coverage_dose1_lag1)/100 +
                                   pop_two*(100 - tc_coverage_dose1_lag2)/100 +
                                   pop_three*(100 - tc_coverage_dose1_lag3)/100 +
                                   pop_four*(100 - tc_coverage_dose1_lag4)/100 +
                                   pop_five*(100 - tc_coverage_dose1_lag5)/100 +
                                   pop_six*(100 - tc_coverage_dose1_lag6)/100 +
                                   pop_seven*(100 - tc_coverage_dose1_lag7)/100 +
                                   pop_eight*(100 - tc_coverage_dose1_lag8)/100 +
                                   pop_nine*(100 - tc_coverage_dose1_lag9)/100 -
                                   cumulative_10yr_cases)) %>%
  ungroup()

summary(df$susceptible_pop1)

# Version 2: Accounting for infection-acquired immunity.. Explicitly accounting for measles cases that happened among children under 10.

df <- df %>%
  group_by(muni_code) %>%
  arrange(year) %>%
  mutate(across(c(births, deaths_U6mo, pop_one:pop_nine, tc_coverage_dose1_lag1:tc_coverage_dose1_lag9, measles_cases, measles_cases_u10), 
                ~replace_na(., 0))) %>%
  mutate(cumulative_previous_u10_cases = lag(rollapply(measles_cases_u10, width = 10, FUN = sum, fill = 0, align = "right", partial = TRUE), default = 0),
         susceptible_pop2 = pmax(0, (births - deaths_U6mo) + 
                                   pop_one*(100 - tc_coverage_dose1_lag1)/100 +
                                   pop_two*(100 - tc_coverage_dose1_lag2)/100 +
                                   pop_three*(100 - tc_coverage_dose1_lag3)/100 +
                                   pop_four*(100 - tc_coverage_dose1_lag4)/100 +
                                   pop_five*(100 - tc_coverage_dose1_lag5)/100 +
                                   pop_six*(100 - tc_coverage_dose1_lag6)/100 +
                                   pop_seven*(100 - tc_coverage_dose1_lag7)/100 +
                                   pop_eight*(100 - tc_coverage_dose1_lag8)/100 +
                                   pop_nine*(100 - tc_coverage_dose1_lag9)/100 -
                                   cumulative_previous_u10_cases)) %>%
  ungroup()

summary(df$susceptible_pop2)

```

##### 1.3.1.3. Making lagged versions of susceptible_pop1 and susceptible_pop2.

```{r}

df <- df %>% 
  mutate(susceptible_pop1_lag1 = dplyr::lag(susceptible_pop1, 1, order_by = year),
         susceptible_pop1_lag2 = dplyr::lag(susceptible_pop1, 2, order_by = year),
         susceptible_pop1_lag3 = dplyr::lag(susceptible_pop1, 3, order_by = year),
         
         susceptible_pop2_lag1 = dplyr::lag(susceptible_pop2, 1, order_by = year),
         susceptible_pop2_lag2 = dplyr::lag(susceptible_pop2, 2, order_by = year),
         susceptible_pop2_lag3 = dplyr::lag(susceptible_pop2, 3, order_by = year))

df <- df[, !names(df) %in% c("susceptible_pop3", "susceptible_pop4")]

```

#### 1.3.2. Map measles susceptible population \[ask for help\].

#### 1.3.3. Show correlation between measles susceptible population and measles cases.

```{r}

# First operationalization.
# Correlation only in current year (not with lag).
cor.test(df$measles_cases, df$susceptible_pop1)
cor.test(df$measles_cases, df$susceptible_pop1_lag1)
cor.test(df$measles_cases, df$susceptible_pop1_lag2)
cor.test(df$measles_cases, df$susceptible_pop1_lag3)

# Second operationalization.
# Correlation only in current year (not with lag).
cor.test(df$measles_cases, df$susceptible_pop2)
cor.test(df$measles_cases, df$susceptible_pop2_lag1)
cor.test(df$measles_cases, df$susceptible_pop2_lag2)
cor.test(df$measles_cases, df$susceptible_pop2_lag3)


```

### 1.4. Show correlation between vaccination rates with different lags and measles cases (*drawing from Kylee!*).

#### 1.4.1. Lagged dose 1 and measles cases.

For dose 1, it seems like lag 2 is still best.

```{r}

# clean up data to work for analysis
reg_data <- df %>% 
  filter(!muni_code %in% c(1504752,  # all established in 2013 - data is a little funky?
                           4212650, 
                           4220000, 
                           4314548, 
                           5006275)
         & year %in% 2008:2023) %>% # complete data for 2008-2020 only
  mutate(region = factor(region),
         state_name = factor(state_name),
         year = factor(year))

# simple negative binomial models for different coverage lags
nb_dose1_lag2 <- glmmTMB(measles_cases ~ coverage_dose1_lag2 + year + offset(log(population)), 
                   family = nbinom2, 
                   data = reg_data)
#summary(nb_dose1_lag2)

nb_dose1_lag3 <- glmmTMB(measles_cases ~ coverage_dose1_lag3 + year + offset(log(population)), 
                   family = nbinom2, 
                   data = reg_data)
#summary(nb_dose1_lag3)

nb_dose1_lag4 <- glmmTMB(measles_cases ~ coverage_dose1_lag4 + year + offset(log(population)), 
                   family = nbinom2, 
                   data = reg_data)
#summary(nb_dose1_lag4)

nb_dose1_lag5 <- glmmTMB(measles_cases ~ coverage_dose1_lag5 + year + offset(log(population)), 
                   family = nbinom2, 
                   data = reg_data)
#summary(nb_dose1_lag5)

nb_dose1_lag6 <- glmmTMB(measles_cases ~ coverage_dose1_lag6 + year + offset(log(population)), 
                   family = nbinom2, 
                   data = reg_data)
#summary(nb_dose1_lag6)

# compare coefficients for each lag
print(map_dfr(paste0("nb_dose1_lag", 2:6), function(model_name) {
  model <- get(model_name)
  lag_num <- gsub("nb_dose1_lag", "", model_name)
  tidy(model) %>%
    filter(term == paste0("coverage_dose1_lag", lag_num))  # Fixed this line too
}))
# 2 year lagged (like coverage in 2010 for the year 2012) looks the biggest

# predict fxn for each lag
pred_fun <- function(model, lag) {
  lag_num <- gsub("lag", "", lag)
  predict_response(model,
                   terms = paste0("coverage_lag", lag_num, " [0:100]"),
                   type = "count",
                   condition = c(population = 100000, year = 2019),
                   interval = "confidence") %>%
    rename(coverage = x) %>% data.frame() %>% mutate(group = lag)
}


pred_fun <- function(model, lag) {
  lag_num <- gsub("lag", "", lag)
  predict_response(model,
                   terms = paste0("coverage_dose1_lag", lag_num, " [0:100]"),  # Added "dose1_"
                   type = "count",
                   condition = c(population = 100000, year = 2019),
                   interval = "confidence") %>%
    rename(coverage = x) %>% data.frame() %>% mutate(group = lag)
}

preds <- purrr::map2_dfr(list(nb_dose1_lag2, nb_dose1_lag3, nb_dose1_lag4, nb_dose1_lag5, nb_dose1_lag6),
                         c("lag2", "lag3", "lag4", "lag5", "lag6"),
                         ~pred_fun(.x, .y))

# plot
ggplot(preds, aes(x = coverage, y = predicted)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  geom_line() +
  facet_wrap(~group, ncol = 3)

# log scale
ggplot(preds, aes(x = coverage, y = predicted)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  geom_line() +
  facet_wrap(~group, ncol = 3) +
  scale_y_log10()

rm(nb_dose1_lag2, nb_dose1_lag3, nb_dose1_lag4, nb_dose1_lag5, nb_dose1_lag6, pred_fun)

```

#### 1.4.2 Lagged dose 2 and measles cases.

For dose 1, it (also) still seems like lag 2 is still best.

Lag 5 is larger, but is using many fewer years of data (since we only have dose 2 data from 2013 onward).

```{r}

# clean up data to work for analysis
reg_data2 <- df %>% 
  filter(!muni_code %in% c(1504752,  # all established in 2013 - data is a little funky?
                           4212650, 
                           4220000, 
                           4314548, 
                           5006275)
         & year %in% 2013:2023) %>% # complete data for 2008-2020 only
  mutate(region = factor(region),
         state_name = factor(state_name),
         year = factor(year))

# simple negative binomial models for different coverage lags
nb_dose2_lag2 <- glmmTMB(measles_cases ~ coverage_dose2_lag2 + year + offset(log(population)), 
                         family = nbinom2, 
                         data = reg_data2)
#summary(nb_dose2_lag2)

nb_dose2_lag3 <- glmmTMB(measles_cases ~ coverage_dose2_lag3 + year + offset(log(population)), 
                         family = nbinom2, 
                         data = reg_data2)
#summary(nb_dose2_lag3)

nb_dose2_lag4 <- glmmTMB(measles_cases ~ coverage_dose2_lag4 + year + offset(log(population)), 
                         family = nbinom2, 
                         data = reg_data2)
#summary(nb_dose2_lag4)

nb_dose2_lag5 <- glmmTMB(measles_cases ~ coverage_dose2_lag5 + year + offset(log(population)), 
                         family = nbinom2, 
                         data = reg_data2)
#summary(nb_dose2_lag5)

nb_dose2_lag6 <- glmmTMB(measles_cases ~ coverage_dose2_lag6 + year + offset(log(population)), 
                         family = nbinom2, 
                         data = reg_data2)
#summary(nb_dose2_lag6)

# compare coefficients for each lag
print(map_dfr(paste0("nb_dose2_lag", 2:6), function(model_name) {
  model <- get(model_name)
  lag_num <- gsub("nb_dose2_lag", "", model_name)
  tidy(model) %>%
    filter(term == paste0("coverage_dose2_lag", lag_num))  # Fixed this line too
}))
# 2 year lagged (like coverage in 2010 for the year 2012) looks the biggest

# predict fxn for each lag
pred_fun <- function(model, lag) {
  lag_num <- gsub("lag", "", lag)
  predict_response(model,
                   terms = paste0("coverage_lag", lag_num, " [0:100]"),
                   type = "count",
                   condition = c(population = 100000, year = 2019),
                   interval = "confidence") %>%
    rename(coverage = x) %>% data.frame() %>% mutate(group = lag)
}


pred_fun <- function(model, lag) {
  lag_num <- gsub("lag", "", lag)
  predict_response(model,
                   terms = paste0("coverage_dose2_lag", lag_num, " [0:100]"),  # Added "dose2_"
                   type = "count",
                   condition = c(population = 100000, year = 2019),
                   interval = "confidence") %>%
    rename(coverage = x) %>% data.frame() %>% mutate(group = lag)
}

preds <- purrr::map2_dfr(list(nb_dose2_lag2, nb_dose2_lag3, nb_dose2_lag4, nb_dose2_lag5, nb_dose2_lag6),
                         c("lag2", "lag3", "lag4", "lag5", "lag6"),
                         ~pred_fun(.x, .y))

# plot
ggplot(preds, aes(x = coverage, y = predicted)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  geom_line() +
  facet_wrap(~group, ncol = 3)

# log scale
ggplot(preds, aes(x = coverage, y = predicted)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  geom_line() +
  facet_wrap(~group, ncol = 3) +
  scale_y_log10()

rm(nb_dose2_lag2, nb_dose2_lag3, nb_dose2_lag4, nb_dose2_lag5, nb_dose2_lag6, pred_fun)

```

## 2. Regression analysis.

### 2.0. Preparation.

```{r}

panel <- pdata.frame(df, index = c("muni_code", "year"))

```

### 2.1. Negative binomial with lagged dose 1 and measles cases (no covariates).

```{r}

model1 <- glmmTMB(measles_cases ~ coverage_dose1_lag2 + offset(log(population)), 
                      data = panel, 
                      family = nbinom2)
summary(model1_tmb)

```

### 2.2. Directed acylcic graph (DAG) to justify covariate selection.

```{r}

dag1 <- dagitty('dag {
bb="0,0,1,1"
"GDP PC" [pos="0.684,0.620"]
"UBS density" [pos="0.499,0.033"]
"doctor density" [pos="0.245,0.095"]
"measles cases" [outcome,pos="0.867,0.379"]
"nurse density" [pos="0.742,0.090"]
"pop density" [pos="0.349,0.621"]
"vaccination coverage" [exposure,pos="0.144,0.368"]
"GDP PC" -> "UBS density"
"GDP PC" -> "doctor density"
"GDP PC" -> "measles cases"
"GDP PC" -> "nurse density"
"GDP PC" -> "vaccination coverage"
"GDP PC" <-> "pop density"
"UBS density" -> "doctor density"
"UBS density" -> "measles cases"
"UBS density" -> "nurse density"
"UBS density" -> "vaccination coverage"
"doctor density" -> "measles cases"
"doctor density" -> "vaccination coverage"
"doctor density" <-> "nurse density"
"nurse density" -> "measles cases"
"nurse density" -> "vaccination coverage"
"pop density" -> "measles cases"
"vaccination coverage" -> "measles cases"
}')

plot(dag1)


```

#### 2.2.1. Correlations among covariates.

```{r}

# Checking correlation between doctors/nurses and UBS density.
cor.test(df$nurses_p100k, df$UBS_p100k) # Positive association between nurse and UBS density.
cor.test(df$doctors_p100k, df$UBS_p100k) # Negative association between doctor and UBS density.

# Checking correlation between doctors/nurses/UBS density and GDP per capita.
cor.test(df$nurses_p100k, df$GDP_PC) # Positive association between nurse density and GDP PC.
cor.test(df$doctors_p100k, df$GDP_PC) # Positive association between doctor density and GDP PC.
cor.test(df$UBS_p100k, df$GDP_PC) # Negative association between UBS density and GDP PC.

cor.test(df$GDP_PC, df$pop_density)

```

### 2.3. Negative binomial with lagged dose 1 and measles cases with covariates.

```{r}

model2.1 <- glmmTMB(measles_cases ~ coverage_dose1_lag2 + UBS_p100k + offset(log(population)), 
                      data = panel, 
                      family = nbinom2)
summary(model2.1)

model2.2 <- glmmTMB(measles_cases ~ coverage_dose1_lag2 + doctors_p100k + UBS_p100k + offset(log(population)), 
                      data = panel, 
                      family = nbinom2)
summary(model2.2)

model2.3 <- glmmTMB(measles_cases ~ coverage_dose1_lag2 + doctors_p100k + UBS_p100k +
                      nurses_p100k + offset(log(population)), 
                      data = panel, 
                      family = nbinom2)
summary(model2.3)

model2.4 <- glmmTMB(measles_cases ~ coverage_dose1_lag2 + doctors_p100k + UBS_p100k +
                      nurses_p100k + GDP_PC + offset(log(population)), 
                      data = panel, 
                      family = nbinom2)
summary(model2.4)

model2.5 <- glmmTMB(measles_cases ~ coverage_dose1_lag2 + doctors_p100k + UBS_p100k +
                      nurses_p100k + GDP_PC + pop_density + offset(log(population)), 
                      data = panel, 
                      family = nbinom2)
summary(model2.5)


```

### 2.4. Negative binomial with lagged dose 1 and measles cases with covariates, region fixed effects.

```{r}

model3.1 <- glmmTMB(measles_cases ~ coverage_dose1_lag2 + UBS_p100k + region + offset(log(population)), 
                      data = panel, 
                      family = nbinom2)
summary(model3.1)

model3.2 <- glmmTMB(measles_cases ~ coverage_dose1_lag2 + doctors_p100k + UBS_p100k + region + offset(log(population)), 
                      data = panel, 
                      family = nbinom2)
summary(model3.2)

model3.3 <- glmmTMB(measles_cases ~ coverage_dose1_lag2 + doctors_p100k + UBS_p100k +
                      nurses_p100k + region + offset(log(population)), 
                      data = panel, 
                      family = nbinom2)
summary(model3.3)

model3.4 <- glmmTMB(measles_cases ~ coverage_dose1_lag2 + doctors_p100k + UBS_p100k +
                      nurses_p100k + GDP_PC + region + offset(log(population)), 
                      data = panel, 
                      family = nbinom2)
summary(model3.4)

model3.5 <- glmmTMB(measles_cases ~ coverage_dose1_lag2 + doctors_p100k + UBS_p100k +
                      nurses_p100k + GDP_PC + pop_density + region + offset(log(population)), 
                      data = panel, 
                      family = nbinom2)
summary(model3.5)

```

### 2.5. Visualizing regression coefficients.

```{r}

# Model lists and names.
models2 <- list(model2.1, model2.2, model2.3, model2.4, model2.5)
model_names2 <- paste0("Model 2.", 1:5)
models3 <- list(model3.1, model3.2, model3.3, model3.4, model3.5)
model_names3 <- paste0("Model 3.", 1:5)

# Function to extract coefficients with confidence intervals
extract_coefs_with_ci <- function(model, model_name) {
  coef_summary <- summary(model)$coefficients$cond
  
  estimates <- coef_summary[, "Estimate"]
  std_errors <- coef_summary[, "Std. Error"]
  
  keep <- !grepl("Intercept|region", names(estimates))
  estimates <- estimates[keep]
  std_errors <- std_errors[keep]
  
  ci_lower <- estimates - 1.96 * std_errors
  ci_upper <- estimates + 1.96 * std_errors
  
  data.frame(
    term = names(estimates),
    estimate = as.numeric(estimates),
    ci_lower = as.numeric(ci_lower),
    ci_upper = as.numeric(ci_upper),
    model = model_name,
    stringsAsFactors = FALSE
  )
}

# Extract coefficients for all models
all_coefs_ci2 <- do.call(rbind, lapply(seq_along(models2), function(i) {
  extract_coefs_with_ci(models2[[i]], model_names2[i])
}))

all_coefs_ci3 <- do.call(rbind, lapply(seq_along(models3), function(i) {
  extract_coefs_with_ci(models3[[i]], model_names3[i])
}))

# Plot function.
plot_coefficients <- function(coef_data, title_suffix) {
  ggplot(coef_data, aes(x = term, y = estimate)) +
    geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                   size = 0.5, color = "blue") +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
    facet_wrap(~ model, scales = "free_y") +
    coord_flip() +
    theme_minimal() +
    labs(title = paste("Model", title_suffix, "Coefficients with 95% Confidence Intervals"),
         x = "Variables", 
         y = "Coefficient Estimate")
}

# Generating and displaying plots
plot2 <- plot_coefficients(all_coefs_ci2, "2")
plot3 <- plot_coefficients(all_coefs_ci3, "3")
print(plot2)
print(plot3)

```

S
